\thesistitle

### 2019-07-30 sections/clonerefactor.tex
Categories

\section{Context Analysis of Clones}\label{chap:contextsetup}
To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the catagories of clones.

@@

\subsubsection{Common Class}
The \textit{Same method} and \textit{Same class} relations share a common refactoring opportunity. Clones of both these catagories, when extracted to a new method, can be placed in the same class. Both of these relations are most favorable for refactoring, as they require a minimal design tradeoff. Furthermore, global variables that are used in the class can be used without having to create method parameters.

@@

\subsubsection{Unrelated}
Clones are unrelated if they share no common class or interface in their inheritance structure. These clones are least favorable when looking at refactoring, because their refactoring will almost always have a major impact on system design. We formulated four catagories of unrelated clones to look into their refactoring opportunities.

>>>>

\section{Context Analysis of Clones}\label{chap:contextsetup}
To be able to refactor code clones, CloneRefactor first maps the context of code clones. We define the following aspects of the clone as its context:
\begin{enumerate}
  \item \textbf{Relation:} The relation of clone instances among each other through inheritance.
  \item \textbf{Location:} Where a clone instance occurs in the code.
  \item \textbf{Contents:} The statements/declarations of a clone instance.
\end{enumerate}
We define categories for each of these aspects and enable CloneRefactor to determine the categories of clones.

@@

\subsubsection{Common Class}
The \textit{Same method} and \textit{Same class} relations share a common refactoring opportunity. Clones of both these categories, when extracted to a new method, can be placed in the same class. Both of these relations are most favorable for refactoring, as they require a minimal design tradeoff. Furthermore, global variables that are used in the class can be used without having to create method parameters.

@@

\subsubsection{Unrelated}
Clones are unrelated if they share no common class or interface in their inheritance structure. These clones are least favorable when looking at refactoring, because their refactoring will almost always have a major impact on system design. We formulated four categories of unrelated clones to look into their refactoring opportunities.

### 2019-07-30 sections/results.tex
Categories

\section{Merging duplicate code through refactoring} \label{sec:refactorability}
\todo{update these results}
In section \ref{sec:refactorabilitysetup} we define catagories regarding the extent to which clones can be refactored through method extraction. Our results are displayed in Table \ref{table:refactorability}.

>>>>

\section{Merging duplicate code through refactoring} \label{sec:refactorability}
\todo{update these results}
In section \ref{sec:refactorabilitysetup} we define categories regarding the extent to which clones can be refactored through method extraction. Our results are displayed in Table \ref{table:refactorability}.
